quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-05-19 paper-quollr.Rmd
Added sentence for main model approach

This paper presents the R package, `quollr`, which is useful for understanding how NLDR warps high-dimensional space and fits the data (`r knitr::asis_output(if (knitr::is_html_output()) { "[Figure 1](#fig-overview)"} else { "Figure \\@ref(fig:overview)"})`).

>>>>

This paper presents the R package, `quollr`, which is useful for understanding how NLDR warps high-dimensional space and fits the data. Starting with an NLDR layout, our approach is to create a wireframe model representation, that can be lifted and displayed in the high-dimensional space (`r knitr::asis_output(if (knitr::is_html_output()) { "[Figure 1](#fig-overview)"} else { "Figure \\@ref(fig:overview)"})`).

### 2025-05-19 paper-quollr.tex
Added sentence for main model approach

This paper presents the R package, \texttt{quollr}, which is useful for understanding how NLDR warps high-dimensional space and fits the data (Figure \ref{fig:overview}).

>>>>

This paper presents the R package, \texttt{quollr}, which is useful for understanding how NLDR warps high-dimensional space and fits the data. Starting with an NLDR layout, our approach is to create a wireframe model representation, that can be lifted and displayed in the high-dimensional space (Figure \ref{fig:overview}).
